GMSE: a general tool for management strategy evaluation

### 2017-09-18 notebook/presentation/GMSE_presentation.Rmd
Revised slides

![](adaptive_management.png)

@@

- What leads to conservation conflict
- How to resolve conservation conflict
- Impact on sustainability of social-ecological systems

@@

@@

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Fox & Madsen 2017 *Ambio* **46(s2)**:170-187](http://doi.org/10.1007/s13280-016-0878-2)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Fox & Abraham 2017 *Ambio* **46(s2)**:188-197](http://doi.org/10.1007/s13280-016-0879-1)

@@

```{r, echo = TRUE}
sim <- gmse(land_ownership = TRUE, stakeholders = 10, observe_type = 1,
            res_death_K = 2000, manage_target = 1000, RESOURCE_ini = 1000,
            user_budget = 5000, manager_budget = 5000, res_consume = 1,
            scaring = TRUE, fixed_mark = 50, fixed_recapt = 300,
            plotting = FALSE);
```

@@

>>>>

![](African_Bush_Elephant.jpg)
<!--- ![](adaptive_management.png) --->

**Image:** [M. M. Karim](https://en.wikipedia.org/wiki/User:Muhammad_Mahdi_Karim)

@@

- What leads to conservation conflict?
- How to resolve conservation conflict?
- Impact on sustainability of social-ecological systems?

@@

<br><br><br><br><br><br><br><br>

@@

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Fox & Madsen 2017 *Ambio* **46(s2)**:170-187](http://doi.org/10.1007/s13280-016-0878-2)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Fox & Abraham 2017 *Ambio* **46(s2)**:188-197](http://doi.org/10.1007/s13280-016-0879-1)

@@

```{r, echo = TRUE}
sim <- gmse(land_ownership = TRUE, stakeholders = 10, RESOURCE_ini = 1000,
            res_death_K = 2000, manage_target = 1000, res_consume = 1,
            user_budget = 5000, manager_budget = 5000, plotting = FALSE,
            scaring = TRUE, culling = TRUE, observe_type = 1, fixed_mark = 50, 
            fixed_recapt = 300);
```

@@

![](GMSE_Logo_Goose_340.png)
